Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-22 lqg-strings.tex
moved the section about the explicit expression for Delta field to main text, made the approppriate changes and changed some stuff in said section

In \autoref{sec:inverse-metric-Polyakov} we explore the Polyakov version of the modified NG action derived from the bimetric analysis and point out its consequences for the equations of motion. Furthermore, we solve the string equations of motion for a particular case of constant-coefficient to find the fundamental modes and derive the Poisson bracket algebra for the modes and constraints. In \autoref{sec:quantum-kg-string} we follow the route of canonical covariant quantization for the solution previously found and discuss the consequences of our area-corrected model regarding the dimensionality of the background spacetime and the presence of negative-norm states (ghosts) in the physical excitations.

@@

@@

If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} explored in sections \ref{sec:modified-ng} and \ref{sec:inverse-metric-Polyakov}, one would end up concluding that either $\Delta _{a b} = 0$ or it's determinant $\Delta = 0$ vanish. This happens because, as we explored in section \ref{sec:ws-kalb-ramond}, $\Delta _{a b}$ is actually related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$, but those actions were actions for the free string, not coupled to said field. The more complete picture would be thus to consider the string now coupled to the Kalb-Ramond field \cite{Tong2009Lectures}
\begin{multline} \label{eqn:area-corrected-K-R-action}
	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \widetilde{\varepsilon}^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) ,
\end{multline}
where we can rewrite $\widetilde{\varepsilon}^{a b}$ in terms of $\Delta ^{a b}$ as
\begin{multline} \label{eqn:area-corrected-K-R-action-v2}
	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) .
\end{multline}
By varying this action \wrt $\Delta ^{c d}$ we get
\begin{equation} \label{}
	\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}
\end{equation}
with $\widetilde{f}$ given by
\begin{multline} \label{eqn:1/f-tilde}
	\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Bigg( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) ,
\end{multline}
where if we take $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$ and $\del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} = \Delta _{a b} / \widetilde{f}$ this simplifies to
\begin{equation} \label{eqn:f-tilde}
	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}} ,
\end{equation}
from which it is easy to see that the pullback of the Kalb-Ramond field $b_{a b} := \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ is given by
\begin{equation} \label{eqn:WS-b-field}
	b_{a b} = - \frac{1}{\dfrac{g}{k \Delta} + 1} \widetilde{\varepsilon}_{a b} ,
\end{equation}
or equivalently that the relation between $\Delta _{a b}$ and $b_{a b}$ is
\begin{equation} \label{eqn:Delta-b-relation}
	\Delta _{a b} = \sqrt{\Delta} \widetilde{\varepsilon}_{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
\end{equation}

>>>>

In \autoref{sec:inverse-metric-Polyakov} we explore the Polyakov version of the modified string action derived from the bimetric analysis and point out its consequences for the equations of motion. We also take a glance at the explicit expression for the $\Delta _{a b}$ field by considering the (area-corrected) string coupled to the Kalb-Ramond field. Furthermore, we solve the string equations of motion for a particular case of constant-coefficient to find the fundamental modes and derive the Poisson bracket algebra for the modes and constraints. In \autoref{sec:quantum-kg-string} we follow the route of canonical covariant quantization for the solution previously found and discuss the consequences of our area-corrected model regarding the dimensionality of the background spacetime and the presence of negative-norm states (ghosts) in the physical excitations.

@@

If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} explored before, one would end up concluding that either $\Delta _{a b} = 0$ or it's determinant $\Delta = 0$ vanish. This happens because, as we explored in section \ref{sec:ws-kalb-ramond}, $\Delta _{a b}$ is actually related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$, but those actions were actions for the free string, not coupled to said field. The more complete picture would be thus to consider the (area-corrected) string now coupled to the Kalb-Ramond field \cite{Tong2009Lectures}
\begin{multline} \label{eqn:area-corrected-K-R-action}
	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \varepsilon ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) ,
\end{multline}
where  we can rewrite $\varepsilon ^{a b}$ in terms of $\Delta ^{a b}$ as
\begin{multline} \label{eqn:area-corrected-K-R-action-v2}
	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) .
\end{multline}
By varying this action \wrt $\Delta ^{c d}$ we get
\begin{equation} \label{eqn:Delta-pullback}
	\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}
\end{equation}
with $\widetilde{f}$ given by
\begin{multline} \label{eqn:1/f-tilde}
	\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Bigg( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) ,
\end{multline}
where if we take $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$ and $\del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} = \Delta _{a b} / \widetilde{f}$ this simplifies to
\begin{equation} \label{eqn:f-tilde}
	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}} ,
\end{equation}
from which it is easy to see that the pullback of the Kalb-Ramond field $b_{a b} := \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ is given by
\begin{equation} \label{eqn:WS-b-field}
	b_{a b} = - \frac{1}{\dfrac{g}{k \Delta} + 1} \varepsilon _{a b} ,
\end{equation}
or equivalently that the relation between $\Delta _{a b}$ and $b_{a b}$ is
\begin{equation} \label{eqn:Delta-b-relation}
	\Delta _{a b} = \sqrt{\Delta} \varepsilon _{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
\end{equation}
We thus see that the pullback of the Kalb-Ramond field is actually a tensor \emph{density} of weight $- 1$, since the coefficient in eq \eqref{eqn:WS-b-field} is a true scalar and the Levi-Civita symbol is itself a density.

@@
